CTest Integration of Sikuli Automated GUI Testing

### 2011-06-17 Documentation/Article.tex
Added GoFigure2 GUI screenshot.  Included description of GoFigure2 software in GoFigure2 example section.

The Sikuli script in Figure~\ref{fig:Gofigure2Example} shows a fragment of a
unit test for the GoFigure2 software~\cite{GoFigure2:Website}. The unit being
tested here is the Toolbar menu which consists of different modes used to
analyze data set plots. In total there are four modes which are represented in
the first line as the vector Toolbar and for each of these modes we want to test
their expected mouse functions. For instance, if we are in the zoom Toolbar
mode then we want the data set plot to zoom in when the user scrolls the mouse
wheel forward. Likewise, if we are in pan mode then we want the plot to move to
the left if the user holds down the left mouse button and moves the mouse to the
left.  Also importantly, we want to see that these two mouse actions are unique
for their respective Toolbar modes; the test will include an assertion that
scrolling forward will zoom in when using zoom mode and will do nothing when
using pan mode.\\

@@

>>>>

The GoFigure2 software~\cite{GoFigure2:Website} (See Figure~\ref{fig:GoFigure2GUI}) is designed to automate 
cell segmentation and tracking for high resolution microscopy data and the Megason Lab uses it to
create cell lineages of developing zebrafish emrbryos. The Sikuli script in Figure~\ref{fig:Gofigure2Example} shows a fragment of a
unit test for our GoFigure2 software.   The unit being
tested here is the Toolbar menu which consists of different modes used to
analyze data set plots. In total there are four modes which are represented in
the first line as the vector Toolbar and for each of these modes we want to test
their expected mouse functions. For instance, if we are in the zoom Toolbar
mode then we want the data set plot to zoom in when the user scrolls the mouse
wheel forward. Likewise, if we are in pan mode then we want the plot to move to
the left if the user holds down the left mouse button and moves the mouse to the
left.  Also importantly, we want to see that these two mouse actions are unique
for their respective Toolbar modes; the test will include an assertion that
scrolling forward will zoom in when using zoom mode and will do nothing when
using pan mode.\\

@@

\begin{figure}[htbp]
 \centering
 \includegraphics[width=0.99\textwidth]{Images/Gofigure2GUI.png}
 % SimpleSikuliExample.png: 1280x1024 pixel, 72dpi, 45.16x36.12 cm, bb=0 0 1280 1024
 \caption{GoFigure2 GUI Interface}
 \label{fig:GoFigure2GUI}
\end{figure}
